Large squeezing in multicomponent trapped Bose-Einstein condensates

### 2013-06-13 large_number_squeezing_with_atoms.tex
Fix some missing \delta's.
Add a few introductory references

>>>>

History: Quantum optics led to creating nonclassical states after the laser was
invented. The advent of the BEC led to the ability to start recreating these types
of states with massive particles. One of the first things that was considered was
quadrature squeezing, as this can be done with intrinsic nonlinearities of the atoms,
which photons don’t have. Quadrature squeezing using nonlinearities has been around
a while (cite Drummond) due to being useful for EPR. Also been shown you can use
it for atom lasers. Possible to use atom nonlinearities to continuously quadrature
squeeze an atom laser [?] To get number squeezing, however, need to mix quadrature
squeezed states or mix a quadrature squeezed state with a coherent local oscillator.
Can be hard to mode match beams of atoms, so doing everything in trap can useful.
That’s why number squeezing (aka spin squeezing) often tends to use a Ramsey-type
interferometry scheme. [4].
These sorts of things have led to experimentally detectable amounts of number
squeezing [10]
